Enhancing Adversarial Robustness for Deep Metric Learning

### 2021-11-07 appendix.tex
tex

@@

	 Why not ResNet-50?
		ttx and video memory.

	 Why compare in theoretical time cost instead of walltime cost?
		Walltime cost does not precisely indicate the true efficiency
		of a defense method, and may even result in unfair comparison.
		isolate the discrepancy from implementation and engineering tricks,
		as well as software / hardware differences.

	 Complete Table for Sec~4.1 Hardness Selection?

	 full data sheet for tab 2?
		\cref{tab:srcdest}

@@

\section{Visualizations}

Visualize robustness through the image retrieval task.

>>>>

\oo{todo}

@@

\noindent\textbf{I. Training Cost}

In the manuscript, the training cost of adversarial training is caluclated as
$\eta+1$, which is a theoretical number of forward-backward propagation
involved in each iteration of the training process.
%
The wall time is not used, because the wall time is noisy, and will be affected
by many irrevevant factors which eventually makes the result uncomparable or
unfair.
%
The factors that affect the wall time for adversarial training include but are
not limited to:
%
(1) GPU Performance. For instance, the wall time reported based on eight Nvidia
A100 GPUs will not be valuable for readers who do not have access to the same
hardware;
%
(2) System load when training, CPU performance, and I/O device performance;
%
(3) Code implementation and engineering tricks. Well-optimized code will
consume less time.
%
Namely, the wall time is a noisy measure of training cost which will render
invalid comparison or unfair comparison.
%
In contrast, the training cost measure ($\eta+1$) in the manuscript has
isolated all irrelevant factors.

~\newline
\noindent\textbf{II. Complete Experimental Results for Tab.~2 in Manuscript}

They can be found in \cref{tab:srcdest} of this supplementary material.

\hrule

@@

\begin{comment}
\section{Visualizations}
Visualize robustness through the image retrieval task.
\end{comment}
